### 2014-03-15 etc/abstract.tex
Fixing the pointed out issues: do/faster/fewer/smarter
Fix unintented %'s
Change Title, Fix spellos
Since we dont provide ranking, remove that portion

% 1.Statetheproblem
Mutation analysis is a well-known method for measuring the quality of
test suites. However, it is computationally intensive compared to
other measures, which makes it hard to use in practice. Choosing a
smaller subset of mutations to run is a simple approach that can
alleviate this problem.  Mutation operator selection has been heavily
researched. Recently, researchers have found that sampling mutants can
achieve accuracy and mutant reduction similar to operator selection.

%2.Saywhyit’saninterestingproblem
However, the statistical support for these conclusions has been limited, due to the small number of subject programs investigated.  The best sampling technique is also an open problem.
% that can be drawn from the previous
%research has been limited due to the small number of subject programs. Further,
%which sampling technique is best is still an open problem that needs to be
%tackled on a much larger range of test subjects.

@@

Our research compares a large number of sampling and operator
selection criteria based on their ability to predict the full mutation
score as well as the consistency of mutation reduction ratios
achieved. Our results provide a ranking that can be used to choose an
appropriate mutation reduction technique by the reduction and level of fidelity to full mutation results required.

>>>>

% 1.Statetheproblem
Mutation analysis is a well-known method for measuring the quality of
test suites. However, it is computationally intensive compared to
other measures, which makes it hard to use in practice. Choosing a
smaller subset of mutations to run is a simple approach that can
alleviate this problem.  Mutation operator selection has been heavily
researched. Recently, researchers have found that sampling mutants can
achieve accuracy and mutant reduction similar to operator selection.
%
%2.Saywhyit’saninterestingproblem
However, the empirical support for these conclusions has been limited, due to the small number of subject programs investigated.  The best sampling technique is also an open problem.
% that can be drawn from the previous
%research has been limited due to the small number of subject programs. Further,
%which sampling technique is best is still an open problem that needs to be
%tackled on a much larger range of test subjects.

@@

Our research compares a large number of sampling and operator
selection criteria based on their ability to predict the full mutation
score as well as the consistency of mutation reduction ratios
achieved. Our results can be used to choose an appropriate mutation
reduction technique by the reduction and level of fidelity to full
mutation results required.
